%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Education}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{} % Degree
{Selected courses} % Institution
{} % Location
{2015 - present} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Essential .NET with C\# for .NET 4.5 - Fall 2014}
\item {Basic Life Insurance Mathematics - Copenhagen University - Spring 2015}
\item {Practical Machine Learning with Functional Programming - NDC London - Spring 2017}
\end{cvitems}
}


\cventry
{PhD in Mathematical modelling} % Degree
{Danish Technical University} % Institution
{Kgs. Lyngby, Denmark} % Location
{Jan. 2011 - Apr. 2014} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Research focused on the mathematical modeling of fluid dynamics, specifically drops on different surfaces; setting up computational FEM models, examining parameter dependency in Matlab, setting up and performing experiments to compare with numerical results.}
\item Visiting researcher at Massachusetts Institute of Technology (MIT) mathematics department, Sep. 2011 - Mar. 2012.
\item Three peer-reviewed published papers on the basis of my thesis, two as first author.
\end{cvitems}
}

\cventry
{Visiting researcher} % Degree
{Massachusetts Institute of Technology (MIT)} % Institution
{Boston, Massachusetts, USA} % Location
{Sep. 2011 - Mar. 2012} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Was a part of the fluid dynamics group at the mathematics department. Participated in numerical and experimental investigations of droplets bouncing on a vibrated fluid surface.}
\item Two papers published on the basis of my visit.
\end{cvitems}
}

\cventry
{MSc in Mathematics and Physics} % Degree
{Roskilde University}
{Roskilde, Denmark} % Location
{Aug. 2003 - Jun. 2010} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Combined degree in Physics and Mathematics.}
\item {Education philosophy emphasizing teaching through problem oriented projects.}
\item Masters thesis on the human cardiovascular system during head-up-tilt experiments. My thesis lead to a published peer-reviewed paper which I co-authored.
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
