%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Technical skills}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvskills}

\cvskill
{Frameworks and tools} % Category
{
\begin{cvitems}
  \vspace{2mm}
\item {Very well versed in .NET, C\#, Visual Studio, Visual Studio Code, Resharper, Mercurial} 
\item Experienced in/with Powershell, Design Patterns, nUnit, GIT, Matlab, Python, Java
\end{cvitems}
}

\cvskill
{Databases} % Category
{
\begin{cvitems}
  \vspace{2mm}
\item {T-SQL, SQL server management studio, Normalforms, datatypes, query building}
\end{cvitems}
}

\cvskill
{Continuous integration} % Category
{
\begin{cvitems}
  \vspace{2mm}
\item {Cruise Control - automated build server}
\end{cvitems}
}

\cvskill
{Project methods \& tools} % Category
{
\begin{cvitems}
  \vspace{2mm}
\item {Agile development, SCRUM}
\item JIRA, Sharepoint, Projectflow
\end{cvitems}
}

\cvskill
{Mathematical modeling} % Category
{
\begin{cvitems}
  \vspace{2mm}
\item {Creating mathematical descriptions of reality}
\item Parameter estimation, parameter grid search
\item ODE solving
\end{cvitems}
}

\cvskill
{Presentation and visualization} % Category
{
\begin{cvitems}
  \vspace{2mm}
\item {I have experience in presenting and visualizing data in a clear and understandable manner.}
\item Experienced user of \LaTeX.
\end{cvitems}
}

 % Skills
\end{cvskills}

\cvsection{Other skills}
\begin{cvskills}
%------------------------------------------------

\cvskill
{Personal} % Category
{
\begin{cvitems}
\item {Outgoing but also self-motivated. I really enjoy working in a team but I also take pride in my own responsibilities.}
\item {Good social skills. If you ask my current colleagues, they would say I am a very well-liked person.}
\item {Curious and interested. I am not afraid to ask questions when there is something I do not understand.}
\item {Logical thinking. I argument and understand through logical reasoning.}
\item {Clear communicator. I am seldom misunderstood and often notice when others are.}
\item {Problem oriented. I think about solutions with the problem as starting point without being limited by subject.}
\item {Quick learner. I pick up new methods or ideas to solve new problems quickly.}
\end{cvitems}} % Skills
 % Skills

% \cvskill
% {Communication} % Category
% {
% \begin{cvitems}
%   \vspace{2mm}
% \item {}
% \end{cvitems}
% } % Skills


%------------------------------------------------

\cvskill
{Languages} % Category
{
\begin{cvitems}
 \vspace{2mm}
\item {Danish and English. Fluent in writing and speech.}
\end{cvitems}
}
\end{cvskills}
